---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Austin Roberts"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Based on the help file, **datasaurus_dozen** has 1846 rows and 3 columns. The dataframe includes the variables: dataset, x, and y. 

### Exercise 2

First we will plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The dataplot shows the shape of a dinosaur, as the relationship between `x` and `y` is not linear it won't make sense to calculate the correlation coefficient.

Calculating the correlation coefficient anyway, we find that

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

We will plot the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()
```

The dataplot shows the shape of a star. As the relationship between `x` and `y` is not linear it won't make sense to calculate the correlation coefficient.

Calculating the correlation coefficient anyway, we find that

```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

The *r* for the star dataset is similar to the *r* of the dino dataset.

### Exercise 4

We will plot the data of the circle dataset:

```{r plot-circle, fig.height=4, fig.width=4}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) + geom_point()
```

The dataplot shows the shape of a circle. As the relationship between `x` and `y` is not linear it won't make sense to calculate the correlation coefficient.

Calculating the correlation coefficient anyway, we find that

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))
```

The *r* for the circle dataset is similar to the *r* of the dino dataset.

### Exercise 5

```{}

```

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)